---
title: "Rmd_Hw03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reference: 
# https://systematicinvestor.wordpress.com/category/factor-model/
# 3-asset example

#=======================================
# Step 1: Import data from excel
#=======================================
# If data has percentage format, then you'd better convert it into numeric format in excel
# First you have to convert factor data into numeric
#===========================================================================================================     
# http://stackoverflow.com/questions/28977777/r-converting-data-frame-of-percentages-from-factor-to-numeric
#==========================================================================================================
# Delete % from data and convert into numeric
#==========================================================================================================
# After conversion, we save the file as 3firmExample_data3.csv
```{r}
firm_data1 = read.csv('3firmExample_data3.csv')
str(firm_data1)
firm_data1$date
```
install.packages("xts")
install.packages("PerformanceAnalytics")
```{r}
library(xts)
library(PerformanceAnalytics)
date1 = as.Date(firm_data1[,1], "%Y/%m/%d")
```
#Convert firm_data1 into time series data: xts
```{r}
firm_data1.xts = as.xts(firm_data1[,-1], order.by = date1)
firm.data1<-coredata(firm_data1.xts)
summary(firm.data1)
skewness(firm.data1)
rbind(apply(firm.data1, 2, summary),
      apply(firm.data1, 2, skewness),
      apply(firm.data1, 2, kurtosis))
```

#====================================================================================
# IF you know the ticker of stocks, then you can 
# download directly from yahoo finance
#=====================================================================================
install.packages("quantmod")
```{r}
library(quantmod)
tickers<-c("JWN", "SBUX", "MSFT")
getSymbols(tickers, from = '2010-12-31', to = '2016-12-31', auto.assign = TRUE)
```

#=================================
# Minimum variance portfolio
#=================================
install.packages("fBasics")
```{r}
library(fBasics)
Sigma = cov(firm_data1[,2:4])
std = sqrt(diag(Sigma))
ones = rep(1,3)     
one.vec = matrix(ones, ncol=1)
a = inv(Sigma)%*%one.vec
b = t(one.vec)%*%a
mvp.w =a / as.numeric(b)
mvp.w
mvp.ret<-sum((mvp.w)*colMeans(firm_data1[,2:4]))
mvp.ret
```

#==================================
# Assume return is specified as 0.06.  
# Try to find its optimal weight and standard deviation (tangency portfolio), 
# expected return and Sharpe ratio.
#=================================
```{r}
mu<-0.06/12
return <- firm_data1[,2:4]
Ax <- rbind(2*cov(return), colMeans(return), rep(1, ncol(return)))
Ax <- cbind(Ax, rbind(t(tail(Ax, 2)), matrix(0, 2, 2)))
b0 <- c(rep(0, ncol(return)), mu, 1)
out<-solve(Ax, b0)
wgt<-out[1:3]
wgt
sum(wgt)
ret.out<-sum(wgt*colMeans(return))
ret.out.annual<-ret.out*12
ret.out.annual
std.out<-sqrt(t(wgt)%*%cov(return)%*%wgt)
std.out.annual<-std.out*sqrt(12)
std.out.annual
```